\bf Faster Neural Machine Translation Inference

### 2018-02-22 fast-beam/fast-beam.tex
fast

We will examine two areas that are critical to fast NMT inference where the models differ significantly from other deep-learning models. We believe the optimizations of these models have been overlooked by the general deep-learning community.

@@

We base our work on the sequence-to-sequence model of ~\citet{D14-1179}. We also choose to focus on the using NMT inference on GPUs. % rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

Our paper follows most closely on from ~\citet{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, specifically the output layer, and the batching algorithm which were not touched on by the previous work.

@@

In models with a small number of classes such as binary classification, the computational effort required is trivial and fast. However, this is not the case for large number of classes such as those found in NMT models.

>>>>

We examine two areas that are critical to fast NMT inference where the models differ significantly from other deep-learning models. We believe the optimizations of these models have been overlooked by the general deep-learning community.

@@

@@

Our paper follows most closely on from ~\citet{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, specifically the output layer, and the batching algorithm which was not touched on by the previous work. Our model is based on that of ~\citet{D14-1179} but our work is applicable to other models and applications. % rather than CPUs as pursued by ~\cite{DBLP:conf/emnlp/Devlin17}.

@@

In models with a small number of classes such as binary classification, the computational effort required is trivial and fast but this is not the case for the large number of classes found in typical NMT models.
